\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-18 using.tex
fuzz things for dave & remove fixmes
more syntax hilight

\begin{figure}[h]
	% FIXME: replace with an image
	\centering
	\colorbox{black}{\color{white}
	{\small
	\begin{tabular}{l}
	\texttt{\hilight{green}{bool}~kern\_current\_extra\_runnable(\hilight{green}{conf\_object\_t}~*cpu)} \\
	\texttt{\{} \\
	\texttt{~~~~\hilight{green}{int}~tcb = \hilight{cyan}{READ\_MEMORY}(cpu, GUEST\_CURRENT\_TCB\_POINTER);} \\
	\texttt{~~~~\hilight{green}{int}~state\_flag = \hilight{cyan}{READ\_MEMORY}(cpu, tcb + GUEST\_TCB\_STATE\_FLAG\_OFFSET);} \\
	\texttt{~~~~\hilight{brown}{return}~state\_flag == GUEST\_TCB\_RUNNABLE;} \\
	\texttt{\}} \\
	\texttt{\hilight{green}{bool}~kern\_ready\_for\_timer\_interrupt(\hilight{green}{conf\_object\_t}~*cpu)} \\
	\texttt{\{} \\
	\texttt{~~~~\hilight{green}{int}~x = \hilight{cyan}{READ\_MEMORY}(cpu, GUEST\_PREEMPTION\_FLAG);} \\
	\texttt{~~~~\hilight{brown}{return}~x == GUEST\_PREEMPTION\_ENABLED;} \\
	\texttt{\}} \\
	\end{tabular}
	}
	}
	\caption{Example implementations of the two functions in \texttt{student.c}.}
	\label{fig:student-c}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\colorbox{black}{\color{white}
	{\small
	\begin{tabular}{l}
	\texttt{\hilight{green}{bool}~kern\_current\_extra\_runnable(\hilight{green}{conf\_object\_t}~*cpu)} \\
	\texttt{\{} \\
	\texttt{~~~~\hilight{green}{int}~tcb = \hilight{cyan}{READ\_MEMORY}(cpu, \hilight{Salmon}{GUEST\_CURRENT\_TCB\_POINTER});} \\
	\texttt{~~~~\hilight{green}{int}~state\_flag = \hilight{cyan}{READ\_MEMORY}(cpu, tcb + \hilight{Salmon}{GUEST\_TCB\_STATE\_FLAG\_OFFSET});} \\
	\texttt{~~~~\hilight{brown}{return}~state\_flag == \hilight{Salmon}{GUEST\_TCB\_RUNNABLE};} \\
	\texttt{\}} \\
	\texttt{\hilight{green}{bool}~kern\_ready\_for\_timer\_interrupt(\hilight{green}{conf\_object\_t}~*cpu)} \\
	\texttt{\{} \\
	\texttt{~~~~\hilight{green}{int}~x = \hilight{cyan}{READ\_MEMORY}(cpu, \hilight{Salmon}{GUEST\_PREEMPTION\_FLAG});} \\
	\texttt{~~~~\hilight{brown}{return}~x == \hilight{Salmon}{GUEST\_PREEMPTION\_ENABLED;}} \\
	\texttt{\}} \\
	\end{tabular}
	}
	}
	\caption{Example implementations of the two functions in \texttt{student.c}.}
	\label{fig:student-c}
\end{figure}
